---
title: "get_outputs_all"
author: "Savannah McNair"
date: "2025-02-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

Load in your paths:
directory_path is where you have saved your summary stats or trial measures data (the folder where the original data is downloaded to)
output_path is where you would like the outputs to get saved
```{r}
#SM set to the location you downloaded the EEG files to. If you are using a Windows computer, you will need to change the direction of the slashes from '\' to '/'
directory_path <- "X:/Projects/hbcd/EEG/Main_Study/CBRAIN_Outputs/DataReleaseIDs/"
output_path <- "Z:/Dropboxes/SMcNair/SMcNair_Playground/HBCD/Data Release/DataRelease_Githhub/test_lasso_deid/"
```

set cwd (current working directory) to file path, get a list of IDs
```{r}
setwd(directory_path) 
cwd <- directory_path
dccids <- list.files()
MMN_files <- intersect(list.files(pattern = "\\ERPSummaryStats.csv$", recursive = TRUE), list.files(pattern = "MMN", recursive = TRUE))
FACE_files <- intersect(list.files(pattern = "\\ERPSummaryStats.csv$", recursive = TRUE), list.files(pattern = "FACE", recursive = TRUE))
VEP_files <- intersect(list.files(pattern = "\\ERPSummaryStats.csv$", recursive = TRUE), list.files(pattern = "VEP", recursive = TRUE))


```

create sheets - these are the sheets this script will output
```{r}
VEP_ERP <- NULL
MMN_ERP <- NULL
FACE_ERP <- NULL
```

for each folder (ID), pull summary stats by task and condition
There is one chunk for each task 

MMN: 
```{r}
#for x (each ID), pull out the MMN ERP data and paste it into a new sheet, storing ID in a new column
for (x in MMN_files) {

 MMN_ERP_file <- paste(cwd, x, sep="")
 x = substring(x, 1, 14)
  if (file.exists(MMN_ERP_file)) {
    MMN_ERP_sheet <- read.csv(MMN_ERP_file)
    for (i in 1:nrow(MMN_ERP_sheet)) {
      MMN_ERP_sheet$ID <- x #paste the DCCID for each row into MMN_ERP_sheet
      MMN_ERP_sheet <- MMN_ERP_sheet %>%
        rename(SME_MMR_t7t8 = 1, #rename cols
               MeanAmp_MMR_t7t8 = 2,
               SME_MMR_f7f8 = 3,
               MeanAmp_MMR_f7f8 = 4,
               SME_MMR_fcz = 5,
               MeanAmp_MMR_fcz = 6)
      row <- MMN_ERP_sheet[i, , drop = FALSE]
      MMN_ERP <- rbind(MMN_ERP, row)
      message(paste("Compiling", x))
    }
  } else {
    message(paste("MMN ERP file not found for", x))
  }
  
}
```

FACE: 
```{r}
#for x (each ID), pull out the FACE ERP data and paste it into a new sheet, storing ID in a new column
for (x in FACE_files) {
 FACE_ERP_file <- paste(cwd, x, sep="")
  x = substring(x, 1, 14)
  if (file.exists(FACE_ERP_file)) {
    FACE_ERP_sheet <- read.csv(FACE_ERP_file)
    for (i in 1:nrow(FACE_ERP_sheet)) {
      FACE_ERP_sheet$ID <- x #paste the DCCID for each row into FACE_ERP_sheet
      FACE_ERP_sheet <- FACE_ERP_sheet %>%
        rename(SME_N290_p8 = 3,
               MeanAmp_N290_p8 = 4, 
               SME_N290_p7 = 5,
               MeanAmp_N290_p7 = 6, 
               SME_P1 = 7,
               MeanAmp_P1 = 8,
               SME_N290_Oz = 9,
               MeanAmp_N290_Oz = 10,
               SME_P400 = 11,
               MeanAmp_P400 = 12,
               SME_N290_Nc = 13,
               MeanAmp_N290_Nc = 14)
      row <- FACE_ERP_sheet[i, , drop = FALSE]
      FACE_ERP <- rbind(FACE_ERP, row)
      message(paste("Compiling", x))
    }
  } else {
    message(paste("FACE ERP file not found for", x))
  }
  
}
```

VEP: 
```{r}
#for x (each ID), pull out the VEP ERP data and paste it into a new sheet, storing ID in a new column
for (x in VEP_files) {
  VEP_ERP_file <- paste(cwd,x, sep="")
   x = substring(x, 1, 14)
  if (file.exists(VEP_ERP_file)) {
    VEP_ERP_sheet <- read.csv(VEP_ERP_file)
    for (i in 1:nrow(VEP_ERP_sheet)) {
      VEP_ERP_sheet$ID <- x #paste the DCCID for each row into VEP_ERP_sheet
      VEP_ERP_sheet <- VEP_ERP_sheet %>%
        rename(SME_N1 = 3,
               Peak_N1 = 4,
               Latency_N1 = 5, 
               MeanAmp_N1 = 6, 
               SME_P1 = 7,
               Peak_P1 = 8,
               Latency_P1 = 9, 
               MeanAmp_P1 = 10, 
               SME_N2 = 11,
               Peak_N2 = 12,
               Latency_N2 = 13, 
               MeanAmp_N2 = 14)
      row <- VEP_ERP_sheet[i, , drop = FALSE]
      VEP_ERP <- rbind(VEP_ERP, row)
      message(paste("Compiling", x))
    }
  } else {
    message(paste("VEP ERP file not found for", x))
  }
  
}
```

output the dataframe containing concatenated power data/summary stats as a csv
```{r}
#pull date as st 
st=format(Sys.time(), "%Y-%m-%d")

#output dfs
write.csv(MMN_ERP,paste(output_path,"MMN_ERP_V03_", st, ".csv", sep=""), row.names=FALSE) #Feel free to change the name of the file to however you would prefer it to be named, as a general example we have chosen "MMN_ERP_V03.csv"
write.csv(FACE_ERP,paste(output_path,"FACE_ERP_V03_", st, ".csv", sep=""), row.names=FALSE) #Feel free to change the name of the file to however you would prefer it to be named, as a general example we have chosen "FACE_ERP_V03.csv"
write.csv(VEP_ERP,paste(output_path,"VEP_ERP_V03_", st, ".csv", sep=""), row.names=FALSE) #Feel free to change the name of the file to however you would prefer it to be named, as a general example we have chosen "VEP_ERP_V03.csv"
```

Output Guide:


MMN: 

Column X: rows for each table (generated by R)
Condition: The condition trials and SME are being reported on (deviant, predeviant, standard for MMN)
SME_200.400_t7t8: Standard measurement error at the t7t8 cluster for the 200-400ms time range
SME_200.400_f7f8: Standard measurement error at the f7f8 cluster for the 200-400ms time range
SME_200.400_fcz: Standard measurement error at the fcz cluster for the 200-400ms time range
ID: participant ID

FACE: 

Column X: rows for each table (generated by R)
Condition: The condition trials and SME are being reported on (deviant, predeviant, standard for MMN)
SME_200.400_t7t8: Standard measurement error at the t7t8 cluster for the 200-400ms time range
SME_200.400_f7f8: Standard measurement error at the f7f8 cluster for the 200-400ms time range
SME_200.400_fcz: Standard measurement error at the fcz cluster for the 200-400ms time range
ID: participant ID

VEP: 

Column X: rows for each table (generated by R)
Condition: Always VEP for this task, as there are not conditions in VEP
SME_40.79_oz: Standard measurement error at the Oz cluster for the 40-79ms time range
SME_80.140_oz: Standard measurement error at the Oz cluster for the 80-140ms time range
SME_141.300_oz: Standard measurement error at the Oz cluster for the 141-300ms time range
ID: participant ID

For more information on measures and outputs consult our documentation, links available in the main Github README
