---
title: "concatenate_trial_measures"
author: "Savannah McNair"
date: "2025-01-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

necessary packages
```{r}
library(dplyr)
```

Load in your paths:
directory_path is where you have saved your summary stats or trial measures data (the folder where the original data is downloaded to)
output_path is where you would like the outputs to get saved
```{r}
#SM set to the location you downloaded the EEG files to. If you are using a Windows computer, you will need to change the direction of the slashes from '\' to '/'
directory_path <- "X:/Projects/hbcd/EEG/Main_Study/CBRAIN_Outputs/DataReleaseIDs/"
output_path <- "Z:/Dropboxes/SMcNair/SMcNair_Playground/HBCD/Data Release/DataRelease_Githhub/test_lasso_deid/"
```

set cwd (current working directory) to file path, get a list of IDs 
```{r}
setwd(directory_path)
cwd <- directory_path
dccids <- list.files()
MMN_files <- intersect(list.files(pattern = "\\ERPTrialMeasures.csv$", recursive = TRUE), list.files(pattern = "MMN", recursive = TRUE))
FACE_files <- intersect(list.files(pattern = "\\ERPTrialMeasures.csv$", recursive = TRUE), list.files(pattern = "FACE", recursive = TRUE))
VEP_files <- intersect(list.files(pattern = "\\ERPTrialMeasures.csv$", recursive = TRUE), list.files(pattern = "VEP", recursive = TRUE))


```

create sheets - these are the sheets this script will output
```{r}
FACE_trialmeasures <- NULL
MMN_trialmeasures <- NULL
VEP_trialmeasures <- NULL
```

for each folder (ID), pull trial stats by task and condition
By Task:

FACE: 
```{r}
#for x (each ID), pull out the trial measure data (by task) and paste it into a new sheet, storing ID in a new column
for (x in FACE_files) {
 FACE_trialmeasures_file <- paste(cwd, x, sep="")
  x = substring(x, 1, 14)
  if (file.exists(FACE_trialmeasures_file)) {
    FACE_trialmeasures_sheet <- read.csv(FACE_trialmeasures_file)
    message(paste("Compiling", x))
    for (i in 1:nrow(FACE_trialmeasures_sheet)) {
      #FACE_trialmeasures_sheet$ID <- x
      FACE_trialmeasures_sheet <- FACE_trialmeasures_sheet %>%
        rename(MeanAmp_N290_p8 = 1,
               MeanAmp_N290_p7 = 5,
               MeanAmp_P1_Oz = 6,             
               MeanAmp_N290_Oz = 7,
               MeanAmp_P400_Oz = 8,
               MeanAmp_Nc_fcz = 9)
      row <- FACE_trialmeasures_sheet[i, , drop = FALSE]
      FACE_trialmeasures <- rbind(FACE_trialmeasures, row)
    }
  } else {
    message(paste("FACE file not found for", x))
  }
}
```

MMN: 
```{r}
#for x (each ID), pull out the trial measure data (by task) and paste it into a new sheet, storing ID in a new column
for (x in MMN_files) {

 MMN_trialmeasures_file <- paste(cwd, x, sep="")
 x = substring(x, 1, 14)
  if (file.exists(MMN_trialmeasures_file)) {
    MMN_trialmeasures_sheet <- read.csv(MMN_trialmeasures_file)
    message(paste("Compiling", x))
    for (i in 1:nrow(MMN_trialmeasures_sheet)) {
      #MMN_trialmeasures_sheet$ID <- x
      MMN_trialmeasures_sheet <- MMN_trialmeasures_sheet %>%
        rename(MeanAmp_MMR_t7t8 = 1,
               MeanAmp_MMR_f7f8 = 5,
               MeanAmp_MMR_fcz = 6)
      row <- MMN_trialmeasures_sheet[i, , drop = FALSE]
      MMN_trialmeasures <- rbind(MMN_trialmeasures, row)
    }
  } else {
    message(paste("MMN file not found for", x))
  }
}
```

VEP: 
```{r}
#for x (each ID), pull out the trial measure data (by task) and paste it into a new sheet, storing ID in a new column
for (x in VEP_files) {
  VEP_trialmeasures_file <- paste(cwd,x, sep="")
   x = substring(x, 1, 14)
  if (file.exists(VEP_trialmeasures_file)) {
    VEP_trialmeasures_sheet <- read.csv(VEP_trialmeasures_file)
    message(paste("Compiling", x))
    for (i in 1:nrow(VEP_trialmeasures_sheet)) {
      #VEP_trialmeasures_sheet$ID <- x
      VEP_trialmeasures_sheet <- VEP_trialmeasures_sheet %>%
        rename(MeanAmp_N1_t7t8 = 1,
               AdaptiveMean_N1_oz = 2,
               Latency_N1_oz = 3,
               MeanAmp_P1_oz = 7,
               AdaptiveMean_P1_oz = 8,
               Latency_P1_oz = 9,
               MeanAmp_N2_oz = 10,
               AdaptiveMean_N2_oz = 11,
               Latency_N2_oz = 12)
      row <- VEP_trialmeasures_sheet[i, , drop = FALSE]
      VEP_trialmeasures <- rbind(VEP_trialmeasures, row)
    }
  } else {
    message(paste("VEP file not found for", x))
  }
}
```

reorder columns
```{r}
FACE_trialmeasures <- FACE_trialmeasures[, c(2,3,4,1,5,6,7,8,9)]
MMN_trialmeasures <- MMN_trialmeasures[, c(2,3,4,1,5,6)]
VEP_trialmeasures <- VEP_trialmeasures[, c(4,5,6,1,2,3,7,8,9,10,11,12)]
```


output the dataframes containing concatenated trial measures as a csv
```{r}
#pull date as st 
st=format(Sys.time(), "%Y-%m-%d")

#output dfs
write.csv(FACE_trialmeasures, paste(output_path, "FACE_trialMeasures_V03_", st, ".csv", sep = ""), row.names=FALSE) 
write.csv(MMN_trialmeasures, paste(output_path, "MMN_trialMeasures_V03_", st, ".csv", sep = ""), row.names=FALSE)
write.csv(VEP_trialmeasures, paste(output_path, "VEP_trialMeasures_V03_", st, ".csv", sep = ""), row.names=FALSE)
```